TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
removed capybara files, added explicit TODOs

SIMD execution on an intermittent system relies on nonvolatile memory instead
of independent registers for each thread. In Chain's case the implementation
would rely on channels for each thread running in the system. In the MIMD
execution model channels could potentially be re-assigned to already allocated
channels because the threads may end at interleaving times. However, in the
SIMD model it is expected that each identical thread is at a comperable point
in execution to the other running threads, and so each thread that may be
run necessitates a new channel allocation. This could lead to an unavoidable
hard limit on the number of threads that can run in an applicatioin which in
turn limits potential applications that are useful on this intermittent device.

@@

Mutexes (Simple, meant for pseudo channels) - Emily\\
Interrupts (mucked with IE flags) - Neil\\
% Interrupt prologue
% Interrupt setup
%\section{Implementation}
%Scheduler Data structures and idempotence (what we broke and why) -NEIL\\
%Mutexes (Simple, meant for pseudo channels) - Emily\\
%Interrupts (mucked with IE flags) - Neil\\
%% Interrupt prologue
%% Interrupt setup

>>>>

SIMD w/ channels (you don't get your own registers...etc -
    just channels, since intermittent)\\

@@

\subsection{Interrupts}
% TODO Interrupts (mucked with IE flags) - Neil\\
% Interrupt prologue
% Interrupt setup

% TODO Mutexes (Simple, meant for pseudo channels) - Emily\\
